InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-02 paper.tex
Section abou the RoBERTa Base OpenAI detector

>>>>

\section{Introdution}

\section{Related work}

\subsection{Generating models}

\subsubsection{Image generating models}

\subsubsection{Text generating models}

\subsection{Detector models}

\subsubsection{Image detector models}

\subsubsection{Text detector models}

The \textbf{RoBERTa Base OpenAI Detector} is the output detector model of GPT-2. It was obtained by fine-tune a RoBERTa base model with the ouputs of the GPT-2 model containing 1,5 Billion parameters. RoBERTa Base OpenAI Detector can be used to classify text, on whether it is likely to be created by the GPT-2 model. It was published by OpenAI, when the weights of the GPT-2 model 1,5 Billion parameter version was released.

\section{Method}

\section{Results}

\section{Discussion}

\section{Conclusion}
